### 2020-11-04 paper/draft1.tex
added paper draft

\documentclass[letterpaper,12pt]{article}

\usepackage[margin=1.5in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{geometry}
\usepackage{physics}
\usepackage{hyperref}
\lstset{
  tabsize=2
}

\renewenvironment{abstract}
 {
  \begin{center}
  \vspace{3em} \bfseries \abstractname\vspace{0em}\vspace{0pt}
  \end{center}
  \list{}{%
    \setlength{\leftmargin}{20mm}% <---------- CHANGE HERE
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \item\relax}
 {\endlist}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\Var}{Var}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\1}{\mathbbm{1}}
\newcommand*{\QED}{\hfill\ensuremath{\square}}%

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\begin{document}

% \title{ELF}
% \author{Anish Thilagar}
% \date{\today}
% \maketitle

% \begin{abstract}

% \end{abstract}

\section{Definitions}
We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_i \in \{0, 1\}$ for $1 \leq i \leq m$. Specifically, let $\theta_i = P(X_i = 1) = 1 - P(X_i = 0)$. For each event event, we draw the outcome for the event $x_i \sim X_i$. We say event $i$ occurred when and only when $x_i = 1$.

define selection mechanism

define accuracy

define proper scoring rule

define truthful mechanism

define accuracy gap

\subsection{Truthfulness using FSD}
Let $p_i$ represent the set of true beliefs $i$ holds over all $m$ events\\\\
Let $y_{i}^{t}$ denote the set of $i$'s reports s.t. for every $k; y_{i,k}^{t} = p_{i,k}$\\\\
Let $y_{i}^{\overline{t}}$ denote the set of $i$'s reports s.t. for every $k; y_{i,k}^{\overline{t}} \ne p_{i,k}$\\\\
Let $G$ denote the cumulative distribution function over a lottery where $y_i = y_{i}^{t}$ and $H$ denote the cumulative distribution function over a lottery where $y_i = y_{i}^{\overline{t}}$\\\\
Lemma 1: A scoring mechanism is truthful iff 
$$\forall x; G(x) \le H(x)$$
$$\exists x; G(x) < H(x)$$ 
which is to say $G$ has first order stochastic dominance over $H$.\\\\
This qualifies as a valid definition for a truthful mechanism because, if $G$ stochastically dominates $H$, then for every possible outcome, given some increasing utility function $U$, any given maximization of $U$ prefers the reports $y_{i}^{t}$ over the reports $y_{i}^{\overline{t}}$. This is to say that truthful reports are always preferred over non-truthful reports which constitutes truthfulness.\\\\\\
SHELF Truthfulness\\\\

\section{Simple average mechanism}
The simplest selection mechanism (and what is often done in practice), we call the simple average mechanism. For this mechanism, we assign each forecaster a score $f_{i, k} = R_q(y_{i, k}, x_k)$ for each event. Then, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$. Finally, we choose the forecaster with the highest cumulative score $\argmax_i F_i$. Each forecaster's cumulative score in this mechanism $\sum_{i=1}^m 1 - (y_{i, j} - x_i)^2$ is an analog for their cumulative accuracy, $m a_j = \sum_{i=1}^m 1 - (y_{i, j} - \theta_j)^2$. However, we will show that this approximation can be flawed.

\subsection{Truthfulness}
show simple counterexample(s?) \\
- single event favors extremes \\
- multiple events can be dominated by single untruthful event when rest are isomorphic \\

\subsection{Accuracy}

Assume forecasters remain honest. For single events, the most extreme forecasters will get selected.

For multiple events, we will see that we get similar accuracy bounds as the SHELF mechanism, assuming the forecasters remain honest. In fact, the main advantage of SHELF is that it is as efficient as the Naive mechanism, but also elicits truthful forecasts.

\section{ELF}
The ELF mechanism, introduced in/by [cite elf paper], improves upon the Naive mechanism, by incentivizing forecasters to be truthful. For each event $k$, we hold a lottery to choose a winner. Forecaster $i$ is chosen with probability
\[ f_{i, k} = \frac{1}{n} + \frac{1}{n} \left(R_q(y_{i, k}, x_k) - \frac{\sum_{j\neq i} R_q(y_{j, k}, x_k)}{n-1} \right)\]
This score is the additively normalized quadratic score among all forecasters. A forecaster increasing their own quadratic score increases the chances they win an event, while decreasing the chances others win that event. Let $w_k$ be the winner of event $k$. The ELF mechanism, $M_l$, then chooses $\argmax_i \sum_{k=1}^m \1(w_k = i)$ as the winner of the competition. Essentially, we give the winner of each event a point, and then pick the forecaster who got the most points.

In [elf paper] Theorem 6, they show that ELF is strictly truthful. In Theorem 8, they also show it is accurate. Specifically, that for an accuracy gap of $\epsilon$, that ELF chooses the most accurate forecaster with probability $ \geq 1 - \delta$ if
\[ m \geq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
For a fixed forecaster accuracy gap and mechanism accuracy, the number of events ELF needs is proportional to $n^2 \ln n$. However, this lower bound is not tight, and can be improved.

Let $F_{i, k}$ be the indicator function for forecaster $i$ winning event $k$. Then, $F_i = \sum_k F_{i, k}$ is the random variable that is the number of events forecaster $i$ wins. The proof of [elf paper] Theorem 8 utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance. However, this is not the case, which leads to an improvement in the lower bound. 
\begin{theorem}[Bernstein's Inequality]
  \label{bernstein}
  Given random variables $X_i$ for $1 \leq i \leq n$ such that $0 \leq X_i \leq 1$ almost surely, let $S = \sum_i X_i$. Then,
  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } \]
\end{theorem}
\begin{theorem}
  \label{elf_bound}
  For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
\end{theorem}
\emph{Proof:} Note that for any single event $k$, every forecaster wins with probability at best $\frac{2}{n}$, and at worst $\frac{1}{n} - \frac{1}{n(n-1)}$ (achieved when $y_i = 1$, $y_{j\neq i} = 0$, and $x_i = 1$). Since $F_{i, k}$ is just a binary random variable, it will have highest variance when it's expectation is as close to $\frac{1}{2}$ as possible. For nontrivially small $n$, this will mean its expectation is $\frac{2}{n}$ (or equivalently $P(F_{i, k} = 1) = \frac{2}{n}$), so its variance will be at most $\frac{2(n-2)}{n^2}$. So we have $\Var(F_{i, k}) \leq \frac{2(n-2)}{n^2} < \frac{2}{n}$.

Since $F_i = \sum_k F_{i, k}$, we have $\Var(F_i) = \sum_k \Var(F_{i, k}) < \sum_k \frac{2}{n} = \frac{2m}{n}$. As shown in [elf paper], for $j\neq i$ we have 
\[ \E[F_i] - \E[F_j] \geq \frac{m \epsilon}{n - 1}\]
Therefore, if $F_j \geq F_i$, (forecaster $j$ beats forecaster $i$), then either forecaster $j$ overperformed their expectation by at least $\frac{m \epsilon}{2(n - 1)}$, or forecaster $i$ underperformed their expectation by $\frac{m \epsilon}{n - 1}$. Specifically, either $\E[F_i] - F_i \geq \frac{m \epsilon}{2(n - 1)}$ or $F_j - \E[F_j] \geq \frac{m \epsilon}{2(n - 1)}$

Applying Theorem \ref{bernstein}, we have
\begin{align*}
    P\left(\left| F_i - \E[F_i]\right| < \frac{m \epsilon}{2(n - 1)} \right) 
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{2m}{n} + \frac{m \epsilon}{6(n - 1)}\right)}} \\
    &< 2 \: e^{\frac{-\left(\frac{m \epsilon}{2(n - 1)}\right)^2 }{2\left(\frac{m}{n-1}(2 + \frac{\epsilon}{6}) \right)}} \\
    &= 2 \: e^{\frac{-\frac{m \epsilon^2}{2(n - 1)} }{(2 + \frac{\epsilon}{6})}} \\
    &< 2 \: e^{-\frac{m \epsilon^2}{6(n - 1)} }  \numberthis \label{elf_bernstein} 
\end{align*}
And similarly for $F_j$. Putting both of those cases together, we have by the union bound
\begin{align*}
  P(F_j \geq F_i) &= P\left(\left(F_j - \E[F_j] < \frac{m \epsilon/62}{2(n - 1)}\right) \cup \left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \right) \\
  &\leq P\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) + P\left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \\
  &\leq 4 \: e^{-\frac{m \epsilon^2}{6(n - 1)} }
\end{align*}
Using the union bound over all $j$, we have
\begin{align*}
  P\left(M_l(y_1, ..., y_n, x) = i\right)
  &= 1 - \sum_{j\neq i} P\left(M_l(y_1, ..., y_n, x) = j\right) \\
  &\geq 1 - \sum_{j\neq i} P\left(F_j \geq F_i\right) \\
  &\geq 1 - 4 (n-1) e^{-\frac{m \epsilon^2}{6(n - 1)}} 
\end{align*}
\hfill\QED

Assigning this probability to $1 - \delta$, we can see that for a fixed $n, \epsilon$, ELF chooses the correct forecaster with probability at least $1 - \delta$ if
\[m \geq \frac{6(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]

\section{SHELF}
For this mechanism, we let the binary random variable $X_{i, k}$ be 1 with probability $R_q(y_{i, k}, x_i)$, and 0 otherwise. Then, for each event $k$ we assign forecaster $i$ the score $f_{i, k} = X_{i, k}$ obtained by sampling this variable. Finally, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$, then chose the forecaster with the highest $F_i$, breaking ties uniformly at random.

\subsection{Truthfulness}
(following section 4.2, theorem 4) For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events. The probability that their final score is 1 will just be their expected score for the single event. Therefore, to maximize their final score, each forecaster must maximize their expected score for the single event. Their score is just $\E_{x \sim \theta}(R_q(y_i, x)) = \E_{x \sim \theta}(1 - (y_i - x)^2)$. This is maximized when $y_i = \theta$, so the mechanism is truthful. (what theorem 4 does) We can also see this directly be noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.

\textbf{Theorem}: SHELF is truthful for $m \geq 1$ events.\\\\
Proof. For each forecaster $j \in [1, n]$ fix forecaster's report.\\\\
S'pose that for some forecaster $i$, $i$'s report on some number of events $k \in [1, m]$ does not maximize their expected score for any of those individual events.\\
Let $k^\prime$ be one of those such events.\\\\
We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to maximize their expected score on each $k$ events. A guiding intuition here would be as follows: The higher the expected score a forecaster has on a given event, the higher the probability that SHELF awards them a point on this specific event, and the only way to maximize one's probability of being selected as the best forecaster is to increase the number of points they are awarded. Therefore, for a single independent event, increasing one's expected score will either increase the probability of being selected as the best forecaster or leave it unchanged, and it does so without altering results of any other event due to the events' independence. In this way, we will show that being truthful for a singular event will always increase one's probability of being selected as the best forecaster. We can then repeat this process for each untruthful report to maximize the probability of being selected as the best forecaster.\\\\
Formally, we will analyze three cases relating to the context provided by the results of $m - 1$ events other than $k^\prime$.\\\\
Let $V(i)$ denote the number of points forecaster $i$ has accrued.\\
Let $f_{i,k}(x)$ denote the probability forecaster $i$ scores a point on event $k$.\\

\begin{enumerate}
    \item Some forecaster $j$ scores at least two more points than $i$, OR $i$ scores at least two more points than any other forecaster.\\
    $$\exists j \in [1,m] \text{ s.t. } j \ne i \text{ and } V(j) - V(i) \geq 2$$ 
    $$OR$$
    $$\forall j \in [1,m] \text{ s.t. } j \ne i; V(i) - V(j) \geq 2$$
    For this case, $i$'s probability of being selected as the best forecaster is either exactly $1$ or $0$. It is also unaffected by $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.\\\\

    \item Some forecaster $j$ scores exactly one more point than $i$, AND no other forecasters score strictly more points than $i$.\\
    $$\exists j \in [1,m] \text{ s.t. } j \neq i \text{ and } V(j) - V(i) = 1$$
    $$AND$$
    $$\forall l \in [1,m] \text{ s.t. } l \neq i \text{ and } l \neq j; V(i) - V(l) \geq 0$$
    For this case, $i$ must seek to maximize $f_{i, k^\prime}(x)$ to have any non-zero probability of being selected as the best forecaster under the SHELF mechanism. Due to the fact that $f_{i, k^\prime}(x) = R_q(y_{i,k^\prime}, x)$ in the SHELF mechanism, $i$'s expectation in number of points is maximized when their respective score is maximized. As a result, $i$, attempting to maximize $f_{i, k^\prime}(x)$, will always prefer to report $p_{i,k^\prime}$ over any other report because that is where their expected score is maximized under the quadratic scoring rule.

    \item No forecasters score more points than $i$, but there is at least one forecaster $j$ that scores the same number of points as $i$ or scores exactly one less point than $i$.
    $$\exists j \in [1,m] \text{ s.t. } j \ne i \text{ and } V(i) - V(j) \in \{0,1\}$$
    In any given configuration, a forecaster's probability of being selected as the best forecaster is maximized when the minimal number of other forecaster have as many points as them. In the SHELF mechanism, any forecaster's probability of scoring a point on a given event is independent of all others. Therefore, there is no action that can be taken to minimize the probability of any competitor's probability of being selected as the best forecaster except strictly increasing one's own point total. In this final case, the only way for $i$ to increase their probability of being chosen as the best forecaster would be to increase the probability of scoring a point in event $k^\prime$. The same logic as case 2 holds here that $i$ would then prefer to report $p_{i,k^\prime}$ and maximize their expected score in $k^\prime$ to increase their expected number of points which will increase their probability of being selected as the best forecaster.
\end{enumerate}
In case 1, $i$'s probability of being selected as the best forecaster is equivalent whether they report truthfully or not. In cases 2 and 3, $i$'s probability of being selected as the best forecaster is strictly greater than reporting anything else. As a result, we can see that under any maximization of our utility function, $i$ will always prefer to report their true belief. Since these three cases are exhaustive and our proposed utility function is increasing, we can now conclude that reporting one's true beliefs has state-wise dominance over reporting outside of one's true beliefs. State-wise dominance is a special case of first-order stochastic dominance. Therefore, reporting true beliefs has first-order stochastic dominance over reporting non-true beliefs. Thus, via lemma 1, SHELF must be truthful.

\subsection{Accuracy}

From proposition 2, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$. Additionally, for a single event, a forecaster's accuracy $a_i$ is by definition just $R_q(y, \theta)$. So, $E_{x \sim \theta}(R_q(y, x)) = a_i + \theta^2 - \theta$. For a single event with probability $\theta$, forecaster $i$'s expected score is $\E_{x \sim \theta} f_i = E_{x \sim \theta}(R_q(y_i, x)) = a_i + \theta^2 - \theta$.

(section 4.3, proposition 5).  For forecaster $i$ to be selected, they either need to have $f_i = 1$, and then be chosen uniformly at random from all others who scored 1, or everyone must score 0 and they will be chosen uniformly at random. In the first case, the expected number of other forecasters who also score 1 is $\sum_{i' \neq i} \E_{x \sim \theta} f_{i'} = \sum_{i' \neq i} (a_{i'} + \theta^2 - \theta) = (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}$. Then, the probability that forecaster $i$ is chosen is 
\[
  P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
\]
In the other case, the probability $i$ wins is just 
\[
  \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
\]

There's probably a better way to do this... Actually coming back to this I'm not even sure that the first step is allowed (using expected number of winners directly instead of summing over cases)

multiple events: (section 5.3, theorem 8)
Let $a_i \geq a_j + \epsilon$ for all $j\neq i$. Like in theorem 8, we first bound the expected number of events won that $i$ exceeds $j$ by. 
\begin{align*}
  \E \left( \sum_{k=1}^m f_{i, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
  &= \left( \sum_{k=1}^m \E f_{i, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
  &= \sum_{k=1}^m \left(\E (f_{i, k}) - \E (f_{j, k})\right)\\
  &= \sum_{k=1}^m \left((a_i + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
  &= \sum_{k=1}^m \left(a_i - a_j\right)\\
  &\geq \sum_{k=1}^m \epsilon\\
  &=m \epsilon
\end{align*}
If $F_j \geq F_i$, then either $\E(F_i) - F_i \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$. By Hoeffding's, we can upper bound the probability of each of these events by $2 e^{-\frac{2 (\frac{m \epsilon}{2})^2}{m}} = 2 e^{\frac{- m \epsilon^2}{2}}$. Using the union bound, the probability that either of those events occurs is twice this, or $4 e^{\frac{- m \epsilon^2}{2}}$.

Using the union bound again over all $j \neq i$, we have 
\[
1 - \delta = P(M(y_1, ..., y_n, x) = i) = 1 - \sum_{j \neq i} P(F_j \geq F_i) = 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
\]
Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when 
\[ m \geq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]

% \begin{thebibliography}{99}

% \end{thebibliography}

\end{document}

### 2020-11-10 paper/draft1.tex
Update draft1.tex

@@
 define proper scoring rule
+Let $p$ denote belief and $y$ denote report
+A scoring rule R is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$
 
 define truthful mechanism
+A scoring mechanism is truthful iff, for all forecasters, their respective probability of being selected as the best overall forecaster is maximized when their reports match their beliefs for all events.
 
@@
 \textbf{Theorem}: SHELF is truthful for $m \geq 1$ events.\\\\
-Proof. For each forecaster $j \in [1, n]$ fix forecaster's report.\\\\
-S'pose that for some forecaster $i$, $i$'s report on some number of events $k \in [1, m]$ does not maximize their expected score for any of those individual events.\\
-Let $k^\prime$ be one of those such events.\\\\
+Proof. For each forecaster $j \in [1, n]$ fix forcaster's report.\\\\
+S'pose that for some forecaster $i$, $i$'s report on some subset of events, where $k \in [1, m]$ denotes the size of this subset, does not maximize their expected score for any of those individual events.\\
+Let $k^\prime$ be one of those events.\\\\
 We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to maximize their expected score on each $k$ events.
 A guiding intuition here would be as follows: The higher the expected score a forecaster has on a given event, the higher the probability that SHELF awards them a point on this specific event, and the only way to maximize one's probability of being selected as the best forecaster is to increase the number of points they are awarded.
-Therefore, for a single independent event, increasing one's expected score will either increase the probability of being selected as the best forecaster or leave it unchanged, and it does so without altering results of any other event due to the events' independence.
+Therefore, for a single independent event, increasing one's expected score will either increase the probability of being selected as the best forecaster or leave it unchanged, and it does so without altering results of any other event.
 In this way, we will show that being truthful for a singular event will always increase one's probability of being selected as the best forecaster.
 We can then repeat this process for each untruthful report to maximize the probability of being selected as the best forecaster.\\\\
-Formally, we will analyze three cases relating to the context provided by the results of $m - 1$ events other than $k^\prime$.\\\\
+Formally, we will analyze three cases relating to the context provided by the $m - 1$ events other than $k^\prime$.\\\\
 Let $V(i)$ denote the number of points forecaster $i$ has accrued.\\
-Let $f_{i,k}(x)$ denote the probability forecaster $i$ scores a point on event $k$.\\
+Let $f_{i,k}$ denote the probability forecaster $i$ scores a point on event $k$.\\
 
@@
     $$\forall j \in [1,m] \text{ s.t. } j \ne i; V(i) - V(j) \geq 2$$
-    For this case, $i$'s probability of being selected as the best forecaster is either exactly $1$ or $0$.
-It is also unaffected by $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.\\\\
+    For this case, $i$'s probability of being selected as the best forecaster is either $1$ or $0$.
+It is also unaffected by being truthful or not in $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.\\\\
 
@@
     $$\forall l \in [1,m] \text{ s.t. } l \neq i \text{ and } l \neq j; V(i) - V(l) \geq 0$$
-    For this case, $i$ must seek to maximize $f_{i, k^\prime}(x)$ to have any non-zero probability of being selected as the best forecaster under the SHELF mechanism.
-Due to the fact that $f_{i, k^\prime}(x) = R_q(y_{i,k^\prime}, x)$ in the SHELF mechanism, $i$'s expectation in number of points is maximized when their respective score is maximized.
-As a result, $i$, attempting to maximize $f_{i, k^\prime}(x)$, will always prefer to report $p_{i,k^\prime}$ over any other report because that is where their expected score is maximized under the quadratic scoring rule.
+    For this case, $i$ must seek to maximize $f_{i,k^\prime}$ to have any non-zero probability of being selected as the best forecaster under the SHELF mechanism. 
+    In the SHELF mechanism, the maximum payout a forecaster can receive for a single event is $1$, and that point is awarded to them with probability exactly equal to their quadratic score.
+Thus, we know a forecaster's expected value for a singular event is exactly their quadratic score.
+Since the quadratic scoring rule is proper, we know that the expectation of a forecaster's quadratic score is maximized when the forecaster is reporting their true beliefs.
+As a result, we can conclude that the only way for $i$ to maximize their probability of receiving a point in $k^\prime$ is to report their true beliefs.
+By reporting their true beliefs, which maximizes the probability that they score another point, $i$ also maximizes the probability of being selected as the best forecaster which, in this context, occurs when only $i$ scores a point and the tie between $j$ and $i$ is broken uniformly via the rules of SHELF.
 
-    \item No forecasters score more points than $i$, but there is at least one forecaster $j$ that scores the same number of points as $i$ or scores exactly one less point than $i$.
+    \item No forecasters score more points than $i$, but there is at least one forecaster $j$ that scores the same number of points as $i$ or scores exactly one less point than $y_i$.
     $$\exists j \in [1,m] \text{ s.t. } j \ne i \text{ and } V(i) - V(j) \in \{0,1\}$$
     In any given configuration, a forecaster's probability of being selected as the best forecaster is maximized when the minimal number of other forecaster have as many points as them.
-In the SHELF mechanism, any forecaster's probability of scoring a point on a given event is independent of all others.
+In the SHELF mechanism, any forecaster's probability of scoring a point on a given event is independent of all other.
 Therefore, there is no action that can be taken to minimize the probability of any competitor's probability of being selected as the best forecaster except strictly increasing one's own point total.
-In this final case, the only way for $i$ to increase their probability of being chosen as the best forecaster would be to increase the probability of scoring a point in event $k^\prime$.
-The same logic as case 2 holds here that $i$ would then prefer to report $p_{i,k^\prime}$ and maximize their expected score in $k^\prime$ to increase their expected number of points which will increase their probability of being selected as the best forecaster.
+In this final case, the only way for $i$ to increase their probability of being chosen as the best forecaster would be to increase the probability of scoring a point in $k^\prime$.
+The same logic as case 2 holds here that $i$ would then prefer to be truthful and maximize their expected score in $k^\prime$ to increase their probability of being selected as the best forecaster.
 \end{enumerate}
-In case 1, $i$'s probability of being selected as the best forecaster is equivalent whether they report truthfully or not.
-In cases 2 and 3, $i$'s probability of being selected as the best forecaster is strictly greater than reporting anything else.
-As a result, we can see that under any maximization of our utility function, $i$ will always prefer to report their true belief.
-Since these three cases are exhaustive and our proposed utility function is increasing, we can now conclude that reporting one's true beliefs has state-wise dominance over reporting outside of one's true beliefs.
-State-wise dominance is a special case of first-order stochastic dominance.
-Therefore, reporting true beliefs has first-order stochastic dominance over reporting non-true beliefs.
-Thus, via lemma 1, SHELF must be truthful.
+
+Since any configuration of the $m-1$ events falls into one of these three cases, we have shown that any forecaster is weakly incentivized to report truthfully.
+To show that any forecaster is strongly incentivized to report truthfully, we simply show that $i$ believes cases 2 or 3 will happen with positive probability.
+Since $y_{j,k} = p_{j,k} \in (0,1) \forall j \forall k$, we know that every forecaster has some uncertainty on each event.
+As a result, we can conclude that $f_{j,k} > 0 \forall j \forall k$.
+We can think of all possible outcomes as the set of all possible binary strings of length $n$, and since $f_{j,k} > 0 \forall j \forall k$ there exists at least one sequence of outcomes strings picked from our set that constitutes cases 2 or 3.
+As a result, there is a positive probability that cases 2 or 3 occur, and thus forecasters are strongly incentivized to report truthfully.
 

### 2020-11-10 paper/draft1.tex
using m_delta

@@
 
+define $m_\delta$
+
 \subsection{Truthfulness using FSD}
@@
 
-In [elf paper] Theorem 6, they show that ELF is strictly truthful.
-In Theorem 8, they also show it is accurate.
-Specifically, that for an accuracy gap of $\epsilon$, that ELF chooses the most accurate forecaster with probability $ \geq 1 - \delta$ if
-\[ m \geq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
-For a fixed forecaster accuracy gap and mechanism accuracy, the number of events ELF needs is proportional to $n^2 \ln n$. However, this lower bound is not tight, and can be improved.
+In [elf paper] Theorem 6, they show that ELF is strictly truthful. In Theorem 8, they also show it is accurate. Specifically, that for an accuracy gap of $\epsilon$, ELF has
+\[ m_\delta \leq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
+For a fixed forecaster accuracy gap and desired mechanism accuracy, the number of events ELF needs is proportional to $n^2 \ln n$.
+However, this upper bound is not tight, and can be lowered significantly.
 
@@
     &= 2 \: e^{\frac{-\frac{m \epsilon^2}{2(n - 1)} }{(2 + \frac{\epsilon}{6})}} \\
-    &< 2 \: e^{-\frac{m \epsilon^2}{6(n - 1)} }  \numberthis \label{elf_bernstein} 
+    &< 2 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }  \numberthis \label{elf_bernstein} 
 \end{align*}
@@
 \begin{align*}
-  P(F_j \geq F_i) &= P\left(\left(F_j - \E[F_j] < \frac{m \epsilon/62}{2(n - 1)}\right) \cup \left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \right) \\
+  P(F_j \geq F_i) &= P\left(\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) \cup \left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \right) \\
   &\leq P\left(F_j - \E[F_j] < \frac{m \epsilon^2}{2(n - 1)}\right) + P\left(\E[F_i] - F_i < \frac{m \epsilon^2}{2(n - 1)} \right) \\
-  &\leq 4 \: e^{-\frac{m \epsilon^2}{6(n - 1)} }
+  &\leq 4 \: e^{-\frac{m \epsilon^2}{5(n - 1)} }
 \end{align*}
@@
   &\geq 1 - \sum_{j\neq i} P\left(F_j \geq F_i\right) \\
-  &\geq 1 - 4 (n-1) e^{-\frac{m \epsilon^2}{6(n - 1)}} 
+  &\geq 1 - 4 (n-1) e^{-\frac{m \epsilon^2}{5(n - 1)}} 
 \end{align*}
@@
 
-Assigning this probability to $1 - \delta$, we can see that for a fixed $n, \epsilon$, ELF chooses the correct forecaster with probability at least $1 - \delta$ if
-\[m \geq \frac{6(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]
+Assigning this probability to $1 - \delta$, we see that for a fixed $n, \epsilon$, ELF will choose the correct forecaster with probability at least $1 - \delta$ if $m$ is large enough for the above inequality to hold.
+Solving it for $m$, we get the minimum such satisfying value
+\[m_\delta \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]
 
@@
 
+\subsection{Truthfulness for a single event}
 (section 4.3, proposition 5).
@@
 
+\subsection{Truthfulness for multiple events}
 multiple events: (section 5.3, theorem 8)
@@
 \]
-Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when 
-\[ m \geq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]
+Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when $m$ is large enough to satisfy the inequality.
+Solving for $m$ gives us the minimum such value, which is an upper bound of $m_\delta$ for SHELF.
+\[ m_\delta \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]
 

### 2020-11-10 paper/draft1.tex
Update draft1.tex

@@
 define $m_\delta$
-
-\subsection{Truthfulness using FSD}
-Let $p_i$ represent the set of true beliefs $i$ holds over all $m$ events\\\\
-Let $y_{i}^{t}$ denote the set of $i$'s reports s.t. for every $k; y_{i,k}^{t} = p_{i,k}$\\\\
-Let $y_{i}^{\overline{t}}$ denote the set of $i$'s reports s.t. for every $k; y_{i,k}^{\overline{t}} \ne p_{i,k}$\\\\
-Let $G$ denote the cumulative distribution function over a lottery where $y_i = y_{i}^{t}$ and $H$ denote the cumulative distribution function over a lottery where $y_i = y_{i}^{\overline{t}}$\\\\
-Lemma 1: A scoring mechanism is truthful iff 
-$$\forall x; G(x) \le H(x)$$
-$$\exists x; G(x) < H(x)$$ 
-which is to say $G$ has first order stochastic dominance over $H$.\\\\
-This qualifies as a valid definition for a truthful mechanism because, if $G$ stochastically dominates $H$, then for every possible outcome, given some increasing utility function $U$, any given maximization of $U$ prefers the reports $y_{i}^{t}$ over the reports $y_{i}^{\overline{t}}$.
-This is to say that truthful reports are always preferred over non-truthful reports which constitutes truthfulness.\\\\\\
-SHELF Truthfulness\\\\
 

### 2020-11-17 paper/draft1.tex
wrote out definitions

@@
 \section{Definitions}
-We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_i \in \{0, 1\}$ for $1 \leq i \leq m$.
-Specifically, let $\theta_i = P(X_i = 1) = 1 - P(X_i = 0)$.
-For each event event, we draw the outcome for the event $x_i \sim X_i$.
-We say event $i$ occurred when and only when $x_i = 1$.
+We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_k \in \{0, 1\}$ for $1 \leq k \leq m$.
+Specifically, let $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$.
+For each event, we draw the outcome for the event $x_k \sim X_k$.
+We say event $k$ occurs when and only when $x_i = 1$.
+There are $n$ participants in the forecasting competition.
+Each forecaster independently submits a vector of predictions $y_i \in [0, 1]^m$, such that $y_{i, k}$ is forecaster $i$'s estimate of $\theta_k$.
+We call these $y_i$ the forecasts of the $i$th forecaster.
 
-define selection mechanism
+A forecasting mechanism $M(y, x)$ maps the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_k)$ to an index $w \in [1, n]$.
+We say that forecaster $w$ wins the competition if $M(y, x) = w$.
+Next, we consider some properties that an ideal mechanism would have.
 
-define accuracy
+We call a mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts.
+Specifically, let $\hat{\theta}_{i, k}$ be forecaster $i$'s belief of the value $\theta_k$.
+We say that $M$ is truthful if for any $y_i \neq \hat \theta_{i}$,
+\[ P(M( (y_1, ..., \hat \theta_i, .., y_n), x ) = i) \geq  P(M( (y_1, ..., \hat y_i, .., y_n), x ) = i)\]
+and we say $M$ is strictly truthful if the strict inequality holds.
+
+Additionally, we would like our mechanism to choose the forecaster with the best predictions.
+We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities.
+Specifically, $a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$.
+An ideal mechanism would choose forecasters with larger accuracies with higher probabilities.
+Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$.
+We call $\epsilon = a^* - \max_{i \neq i^*} a_i$ the accuracy gap.
+$\epsilon$ is the difference in accuracy between the best and second best forecaster.
+
+For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$.
+Specifically, for any $m > m_\delta(M, n, \epsilon)$, $P(M(y, x) \neq i^*) \leq \delta$.
+$m_\delta$ gives us a measure of how many events are needed for a mechanism to stably pick the best forecaster.
+We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.
 
@@
 A scoring rule R is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$
-
-define truthful mechanism
-A scoring mechanism is truthful iff, for all forecasters, their respective probability of being selected as the best overall forecaster is maximized when their reports match their beliefs for all events.
-
-define accuracy gap
-
-define $m_\delta$
 

### 2020-11-17 paper/draft1.tex
added citation and fixed formatting throughout

@@
 % \end{abstract}
+\section{Name???}
+- SHELF\\
+- GNOME\\
+- ???
+
+keywords: event, forecast, voting
+
+EFV
 
 \section{Definitions}
+The definitions borrow heavily in both content and organization from previous work \cite{elf}.
+
 We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_k \in \{0, 1\}$ for $1 \leq k \leq m$.
@@
 \section{Simple average mechanism}
-The simplest selection mechanism (and what is often done in practice), we call the simple average mechanism.
+A simple selection mechanism that is often done in practice, we will call the simple average mechanism $M_s$.
 For this mechanism, we assign each forecaster a score $f_{i, k} = R_q(y_{i, k}, x_k)$ for each event.
 Then, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$.
-Finally, we choose the forecaster with the highest cumulative score $\argmax_i F_i$.
-Each forecaster's cumulative score in this mechanism $\sum_{i=1}^m 1 - (y_{i, j} - x_i)^2$ is an analog for their cumulative accuracy, $m a_j = \sum_{i=1}^m 1 - (y_{i, j} - \theta_j)^2$.
-However, we will show that this approximation can be flawed.
+Finally, we choose the forecaster with the highest cumulative score $M_s(y, x) = \argmax_i F_i$.
+The idea of this mechanism is that each forecaster's final score in this mechanism is $F_i = \sum_{i=1}^m 1 - (y_{i, j} - x_i)^2$ is an analog for their cumulative accuracy, $m a_i = \sum_{k=1}^m 1 - (y_{i, k} - \theta_k)^2$.
+Therefore, the forecaster with the highest score will correlate to the forecaster with the highest accuracy.
+However, we will show that this is not necessarily the case.
 
@@
 \subsection{Accuracy}
+Even though $M_s$ is not truthful, we assume that forecasters still report their true beliefs $\hat \theta_i$.
+For a single event, the most extreme forecasters will always get selected.
+For example, if the single outcome is $x = 0$, the forecaster with the minimum $\hat \theta_i $ will have the highest score, so they will always win.
+Similarly if $x = 1$, the highest belief forecaster will always win.
 
-Assume forecasters remain honest. For single events, the most extreme forecasters will get selected.
-
-For multiple events, we will see that we get similar accuracy bounds as the SHELF mechanism, assuming the forecasters remain honest.
-In fact, the main advantage of SHELF is that it is as efficient as the Naive mechanism, but also elicits truthful forecasts.
+However, for multiple events, the averaging starts to favor more forecasters.
+We will see that we get a similar $m_\delta$ as the SHELF mechanism introduced later, assuming the forecasters remain truthful.
+In fact, the main advantage of SHELF is that it is as efficient as $M_s$ while also being truthful.
 
 \section{ELF}
-The ELF mechanism, introduced in/by [cite elf paper], improves upon the Naive mechanism, by incentivizing forecasters to be truthful.
+\newcommand{\elf}{M_{\mathrm{ELF}}}
+The ELF mechanism $\elf$ \cite{elf}, improves upon $M_s$, by incentivizing forecasters to be truthful.
 For each event $k$, we hold a lottery to choose a winner.
@@
 Let $w_k$ be the winner of event $k$.
-The ELF mechanism, $M_l$, then chooses $\argmax_i \sum_{k=1}^m \1(w_k = i)$ as the winner of the competition.
-Essentially, we give the winner of each event a point, and then pick the forecaster who got the most points.
+Then we choose the forecaster $\elf(y, x) = \argmax_i \sum_{k=1}^m \1(w_k = i)$ as the winner of the competition.
+Essentially, we give the winner of each event lottery a point, and then pick the forecaster who got the most points as the overall winner.
 
-In [elf paper] Theorem 6, they show that ELF is strictly truthful. In Theorem 8, they also show it is accurate. Specifically, that for an accuracy gap of $\epsilon$, ELF has
-\[ m_\delta \leq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
-For a fixed forecaster accuracy gap and desired mechanism accuracy, the number of events ELF needs is proportional to $n^2 \ln n$.
-However, this upper bound is not tight, and can be lowered significantly.
+In Theorem 6 of \cite{elf}, it is proven that $\elf$ is strictly truthful. In Theorem 8 of the same paper, they also upper bound $m_\delta$ by showing 
+\[ m_\delta(\elf, n, \epsilon) \leq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
+For a fixed forecaster accuracy gap and desired mechanism accuracy, the number of events ELF needs to consistently choose the right forecaster is proportional to $\frac{1}{\epsilon^2} n^2 \ln n$.
+However, this upper bound is not tight.
 
-Let $F_{i, k}$ be the indicator function for forecaster $i$ winning event $k$.
+Let $F_{i, k}$ be the indicator function for forecaster $i$ winning the lottery for event $k$.
 Then, $F_i = \sum_k F_{i, k}$ is the random variable that is the number of events forecaster $i$ wins.
-The proof of [elf paper] Theorem 8 utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance.
-However, this is not the case, which leads to an improvement in the lower bound.
+The proof of Theorem 8 \cite{elf} utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance.
+However, this is not the case, and utilizing that fact gives an improvement in the lower bound.
 \begin{theorem}[Bernstein's Inequality]
@@
   \label{elf_bound}
-    For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
+    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$
+    % For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
 \end{theorem}
@@
 \end{align*}
-\hfill\QED
 
@@
 \[m_\delta \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right) \]
+\hfill\QED
 
 \section{SHELF}
+\newcommand{\shelf}{M_{\mathrm{SHELF}}}
+
 For this mechanism, we let the binary random variable $X_{i, k}$ be 1 with probability $R_q(y_{i, k}, x_i)$, and 0 otherwise.
 Then, for each event $k$ we assign forecaster $i$ the score $f_{i, k} = X_{i, k}$ obtained by sampling this variable.
-Finally, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$, then chose the forecaster with the highest $F_i$, breaking ties uniformly at random.
+Finally, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$, then chose the forecaster with the highest score $\shelf(y, x) = \argmax_i F_i$, breaking ties uniformly at random.
 
 \subsection{Truthfulness}
-(following section 4.2, theorem 4) For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events.
+For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events.
 The probability that their final score is 1 will just be their expected score for the single event.
@@
 
-\textbf{Theorem}: SHELF is truthful for $m \geq 1$ events.\\\\
-Proof. For each forecaster $j \in [1, n]$ fix forcaster's report.\\\\
+\begin{theorem}
+  \label{shelf_truthful}
+    $\shelf$ is truthful for $m \geq 1$ events.
+\end{theorem}
+\emph{Proof:} For each forecaster $j \in [1, n]$ fix forcaster's report.
+
 S'pose that for some forecaster $i$, $i$'s report on some subset of events, where $k \in [1, m]$ denotes the size of this subset, does not maximize their expected score for any of those individual events.\\
-Let $k^\prime$ be one of those events.\\\\
+Let $k^\prime$ be one of those events.
+
 We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to maximize their expected score on each $k$ events.
@@
 We can then repeat this process for each untruthful report to maximize the probability of being selected as the best forecaster.\\\\
-Formally, we will analyze three cases relating to the context provided by the $m - 1$ events other than $k^\prime$.\\\\
+Formally, we will analyze three cases relating to the context provided by the $m - 1$ events other than $k^\prime$.
+
 Let $V(i)$ denote the number of points forecaster $i$ has accrued.\\
@@
     For this case, $i$'s probability of being selected as the best forecaster is either $1$ or $0$.
-It is also unaffected by being truthful or not in $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.\\\\
+It is also unaffected by being truthful or not in $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.
 
@@
 
-From proposition 2, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$.
+% From Proposition 2 of \cite{elf}, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$.
 Additionally, for a single event, a forecaster's accuracy $a_i$ is by definition just $R_q(y, \theta)$.
@@
 
-\subsection{Truthfulness for a single event}
-(section 4.3, proposition 5).
+% \subsection{Truthfulness for a single event}
+% (section 4.3, proposition 5).
 For forecaster $i$ to be selected, they either need to have $f_i = 1$, and then be chosen uniformly at random from all others who scored 1, or everyone must score 0 and they will be chosen uniformly at random.
@@
 Then, the probability that forecaster $i$ is chosen is
-\[
-  P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
-\]
-In the other case, the probability $i$ wins is just 
-\[
-  \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
-\]
+% \[
+%   P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
+% \]
+% In the other case, the probability $i$ wins is just 
+% \[
+%   \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
+% \]
 
-There's probably a better way to do this... Actually coming back to this I'm not even sure that the first step is allowed (using expected number of winners directly instead of summing over cases)
+% There's probably a better way to do this... Actually coming back to this I'm not even sure that the first step is allowed (using expected number of winners directly instead of summing over cases)
 
-\subsection{Truthfulness for multiple events}
-multiple events: (section 5.3, theorem 8)
-Let $a_i \geq a_j + \epsilon$ for all $j\neq i$. Like in theorem 8, we first bound the expected number of events won that $i$ exceeds $j$ by. 
+% \subsection{Truthfulness for multiple events}
+\begin{theorem}
+  \label{shelf_bound}
+    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$
+\end{theorem}
+\emph{Proof:} This proof is a slight modification of the proof of Theorem 8 in \cite{elf}.
+
+We first bound the difference in the expected number of wins of $i^*$ and $j$, for any $j \neq i^*$. 
 \begin{align*}
-  \E \left( \sum_{k=1}^m f_{i, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
-  &= \left( \sum_{k=1}^m \E f_{i, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
-  &= \sum_{k=1}^m \left(\E (f_{i, k}) - \E (f_{j, k})\right)\\
-  &= \sum_{k=1}^m \left((a_i + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
-  &= \sum_{k=1}^m \left(a_i - a_j\right)\\
+  \E \left( \sum_{k=1}^m f_{i^*, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
+  &= \left( \sum_{k=1}^m \E f_{i^*, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
+  &= \sum_{k=1}^m \left(\E (f_{i^*, k}) - \E (f_{j, k})\right)\\
+  &= \sum_{k=1}^m \left((a_{i^*} + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
+  &= \sum_{k=1}^m \left(a_{i^*} - a_j\right)\\
   &\geq \sum_{k=1}^m \epsilon\\
@@
 \end{align*}
-If $F_j \geq F_i$, then either $\E(F_i) - F_i \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$.
+If $F_j \geq F_{i^*}$, then either $\E(F_{i^*}) - F_{i^*} \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$.
 By Hoeffding's, we can upper bound the probability of each of these events by $2 e^{-\frac{2 (\frac{m \epsilon}{2})^2}{m}} = 2 e^{\frac{- m \epsilon^2}{2}}$.
@@
 Using the union bound again over all $j \neq i$, we have 
-\[
-1 - \delta = P(M(y_1, ..., y_n, x) = i) = 1 - \sum_{j \neq i} P(F_j \geq F_i) = 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
-\]
+\begin{align*}
+  P(\shelf(y, x) = i) &= P(F_{i^*} > F_j \quad \forall j \neq i^*) \\
+                      &\geq 1 - \sum_{j\neq i^*} P(F_{i^*} \leq F_j) \\
+                      &= 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
+\end{align*}
+
 Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when $m$ is large enough to satisfy the inequality.
-Solving for $m$ gives us the minimum such value, which is an upper bound of $m_\delta$ for SHELF.
-\[ m_\delta \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]
+Therefore
+\[ m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]
+\hfill \QED
 
-% \begin{thebibliography}{99}
+Comparing this to the result of Theorem \ref{elf_bound}, we see that $\shelf$ is much more efficient than $\elf$.
+We can also directly apply the proof of Theorem \ref{shelf_bound} to $M_s$, since the mean and variance of $F_i$ is the same in both cases.
+Therefore, $m_\delta(\shelf, n, \epsilon) = m_\delta(M_s, n, \epsilon)$.
 
-% \end{thebibliography}
+\begin{thebibliography}{99}
+\bibitem{elf} Witkowski, Freeman  \emph{Incentive-Compatible Forecasting Competitions} \url{https://las.inf.ethz.ch/files/witkowski-etal-aaai2018.pdf}.
+
+\end{thebibliography}
 

### 2020-11-17 paper/draft1.tex
Update draft1.tex

@@
 
-\section{Definitions}
-The definitions borrow heavily in both content and organization from previous work \cite{elf}.
+\section{Model and Definitions}
+Our model will consist of $n$ forecasters s.t.
+$n \ge 2$ where $i \in [1,n]$ denotes the $i$th forecaster, $m$ independent events where $k \in [1,m]$ denotes the $k$th event.
+Each event $k \in [1,m]$ will be associated with a random variable $X_k$.
+$X_k = 1$ will denote that event $k$ occurred, and, likewise, $X_k = 0$ will denote event $k$ did not occur.
+$\forall k \in [m] \exists \theta_k$ s.t.
+$\theta_k$ denotes the true, unknown probability of event $k$ occurring;  $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$.
+We will denote each outcome drawn as $x_i \sim X_i$.
+For each forecaster $i$, we denote their true belief that event $k$ will occur as $\hat{\theta}_{i,k} \in (0,1)$.
+We then denote $y_{i,k} \in [0,1]$ as the actual report forecaster $i$ makes for event $k$.
+Note that $y_{i,k}$ need not equal $\hat{\theta}_{i,k}$.
+\\
 
-We model a forecasting competition as $m$ independent events denoted by the independent binary random variables $X_k \in \{0, 1\}$ for $1 \leq k \leq m$.
-Specifically, let $\theta_k = P(X_k = 1) = 1 - P(X_k = 0)$.
-For each event, we draw the outcome for the event $x_k \sim X_k$.
-We say event $k$ occurs when and only when $x_i = 1$.
-There are $n$ participants in the forecasting competition.
-Each forecaster independently submits a vector of predictions $y_i \in [0, 1]^m$, such that $y_{i, k}$ is forecaster $i$'s estimate of $\theta_k$.
-We call these $y_i$ the forecasts of the $i$th forecaster.
+After every event $k \in [1,m]$ has occurred, and thus each forecaster has reported $y_{i,k} \forall i f\forall k$, a mechanism will select exactly one forecaster from the set of $[n]$ as the 'best forecaster'.\\
 
-A forecasting mechanism $M(y, x)$ maps the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_k)$ to an index $w \in [1, n]$.
-We say that forecaster $w$ wins the competition if $M(y, x) = w$.
-Next, we consider some properties that an ideal mechanism would have.
+\textbf{Definition 1: Forecaster Selection Mechanism:}\\
+Some mechanism $M(y, x)$ that maps the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_k)$ to an index $w \in [1, n]$.
+We say that forecaster $w$ wins the competition if $M(y, x) = w$.\\
 
-We call a mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts.
-Specifically, let $\hat{\theta}_{i, k}$ be forecaster $i$'s belief of the value $\theta_k$.
-We say that $M$ is truthful if for any $y_i \neq \hat \theta_{i}$,
+We call a forecaster selection mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts.\\
+
+\textbf{Definition 2: Truthful:}\\
+$M$ is truthful iff $\forall i \in [n]$, $\forall \hat{\theta}_i$, $\forall y^{\prime}_i \neq \hat{\theta}_i$, and $\forall y_j s.t. j \neq i$,
 \[ P(M( (y_1, ..., \hat \theta_i, .., y_n), x ) = i) \geq  P(M( (y_1, ..., \hat y_i, .., y_n), x ) = i)\]
-and we say $M$ is strictly truthful if the strict inequality holds.
+\textbf{Note:} $M$ is strictly truthful if the strict inequality inequality holds.\\
 
 Additionally, we would like our mechanism to choose the forecaster with the best predictions.
-We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities.
-Specifically, $a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$.
-An ideal mechanism would choose forecasters with larger accuracies with higher probabilities.
-Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$.
-We call $\epsilon = a^* - \max_{i \neq i^*} a_i$ the accuracy gap.
-$\epsilon$ is the difference in accuracy between the best and second best forecaster.
+We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities.\\
+
+\textbf{Definition 3: Accuracy:}\\
+$a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$.\\
+
+An ideal mechanism would choose forecasters with larger accuracies with higher probabilities. Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$.\\
+
+\textbf{Definition 4: Accuracy Gap:}\\
+$\epsilon = a^* - \max_{i \neq i^*} a_i$ denote the accuracy gap.\\
 
@@
 $m_\delta$ gives us a measure of how many events are needed for a mechanism to stably pick the best forecaster.
-We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.
+We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.\\
 
-define proper scoring rule
-Let $p$ denote belief and $y$ denote report
-A scoring rule R is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$
+Similar to work in [ELF Citation], we will focus on using the \textbf{proper scoring rule}, the \textbf{quadratic scoring rule} in our forecaster selection mechanism.\\
+
+\textbf{Definition 5: Proper Scoring Rule}:\\
+Scoring rule, $R$ is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$\\
+
+\textbf{Definition 6: Quadratic Scoring Rule}:\\
+$R_q = 1 - (y - x)^2$; Where $x$ denotes the observed outcome, and $y$ denotes the report.
 
@@
 \subsection{Truthfulness}
+Note: The following analysis is inspired by and follows the work done in [ELF Citation].\\\\
 For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events.

### 2020-11-17 paper/draft1.tex
Update draft1.tex

@@
 
-Similar to work in [ELF Citation], we will focus on using the \textbf{proper scoring rule}, the \textbf{quadratic scoring rule} in our forecaster selection mechanism.\\
+Similar to work in \cite{elf}, we will focus on using the \textbf{proper scoring rule}, the \textbf{quadratic scoring rule} in our forecaster selection mechanism.\\
 
@@
 \subsection{Truthfulness}
-Note: The following analysis is inspired by and follows the work done in [ELF Citation].\\\\
+Note: The following analysis is inspired by and follows the work done in \cite{elf}.\\\\
 For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events.

### 2020-11-17 paper/draft1.tex
elf lower bound

@@
 
+\begin{theorem}
+  \label{elf_lower_bound}
+    For $\delta < \frac{1}{2}$, $m_\delta(\elf, n, \epsilon) > n \log n$
+\end{theorem}
+\emph{Proof:} Pick some $\delta < \frac{1}{2}$ and consider the case where $m = n \log n$ and $\theta_k = 1$ for every event.
+Let $y_{1, k} = 1$ and $y_{i, k} = 0$ for every $i > 1$.
+Therefore, forecaster 1 always forecasts correctly and has a quadratic score $R_q(1, 1) = 1$ for each event, while everyone else is wrong and has a quadratic score of $R_q(0, 1) = 0$ for each event.
+Then, $a_1 = 1$, and $a_i = 0$ for $i > 1$, so we have the worst possible accuracy gap $\epsilon = 1$.
+
+For every event, forecaster 1's score will be 
+\begin{align*}
+  f_1 &= \frac{1}{n}\left(1 + R_q(y_1, 1) - \frac{1}{n-1} \sum_{j \neq i} R_q(y_j, x) \right) \\
+      &= \frac{1}{n}\left(1 + 1 - \frac{1}{n-1} \sum_{j \neq i} 0 \right)\\
+      &= \frac{2}{n}
+\end{align*}
+Since all the other forecasters are symmetric, their $f_i$ must all be the same, and since they sum to 1, we must have $f_i = \frac{n-2}{n(n-1)} < \frac{1}{n}$.
+
+We can reframe the way winners are chosen for each event.
+Instead of holding a lottery, we first flip a coin that gives forecaster 1 a win with probability $\frac{2}{n}$.
+If it does not give them the win, we run a normal lottery for the remaining forecasters, where they each have probability $\frac{1}{n-1}$ of winning.
+This gives them an overall probability of $\frac{n-2}{n(n-1)}$ to win each event, so it is the same the original lottery.
+
+Since all the events are uniform, the expected number of lotteries forecaster 1 will win is $m f_1 = \frac{2m}{n} = 2 \log n$.
+Specifically, their wins will follow the Bernoulli distribution $B(n, \frac{2}{n})$.
+With some probability $C_1 = P(B(n, \frac{2}{n}) < 2\log n) \approx \frac{1}{2}$, forecaster 1 will win less events than expected.
+
+The distribution of wins for the remaining forecasters will follow a uniform multinomial distribution.
+Specifically, we can model it with Balls and Bins.
+Let $M$ be the maximum number of wins of any of the remaining forecasters.
+\begin{lemma}
+    $P(M > 2 \log n) = 1 - o(1)$.
+\end{lemma}
+\emph{Proof:}
+From Theorem 1 of \cite{bnb}, we know that for $m = n \log n$, $P(M > k_\alpha) = 1 - o(1) > C_2$ for some constant $C_2$, where $c = \frac{m}{n\log n}$, $k_\alpha = (d_c - 1 + \alpha) \log n$, and $0 < 1 < \alpha$, such that $d_c$ is the larger solution of $1 + x(\log c - \log x + 1) - c= 0$.
+
+In our case, $c = 1$, so $d_c$ is the solution to $x (1 - \log x) = 0$.
+Therefore, $d_c = e$.
+Since this inequality holds for any $\alpha$, we let $\alpha = 3 - e$.
+Plugging in both values gives us $k_\alpha = 2 \log n$, so $P(M > 2 \log n) = 1 - o(1)$.
+\hfill \QED
+
+Using the lemma, for any $C_2 < 1$ and sufficiently large $n$, $P(M > 2 \log n) > C_2$. We choose some $C_2 > 2\delta$. Now, the probability that forecaster 1 is not chosen is at least
+\[
+  P(B(n, \frac{2}{n}) < 2\log n) \times P(M > 2 \log n) > \frac{1}{2} \times 2\delta = \delta
+\]
+Therefore, it is not true that for any $n$, $\epsilon$, $P(\elf(y, x) \neq i^*) \leq \delta$ when $m = n \log n$. Therefore, $m_\delta(\elf, n, \epsilon) > n \log n$. 
+\hfill \QED
+
 \section{SHELF}
@@
 
+\bibitem{bnb} Raab, Steger  \emph{“Balls into Bins” — A Simple and Tight Analysis} \url{http://www.dblab.ntua.gr/~gtsat/collection/scheduling/Balls%20into%20Bins%20A%20Simple%20and%20Tight%20Anal.pdf}.
+
 \end{thebibliography}

### 2020-11-17 paper/draft1.tex
formatting fun

@@
 Note that $y_{i,k}$ need not equal $\hat{\theta}_{i,k}$.
-\\
 
-After every event $k \in [1,m]$ has occurred, and thus each forecaster has reported $y_{i,k} \forall i f\forall k$, a mechanism will select exactly one forecaster from the set of $[n]$ as the 'best forecaster'.\\
+After every event $k \in [1,m]$ has occurred, and thus each forecaster has reported $y_{i,k} \forall i f\forall k$, a mechanism will select exactly one forecaster from the set of $[n]$ as the 'best forecaster'.
 
-\textbf{Definition 1: Forecaster Selection Mechanism:}\\
-Some mechanism $M(y, x)$ that maps the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_k)$ to an index $w \in [1, n]$.
-We say that forecaster $w$ wins the competition if $M(y, x) = w$.\\
+\begin{definition}
+  \label{mechanism}
+  A \textbf{selection mechanism} $M(y, x)$ is a map from the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_m)$ to an index $w \in [1, n]$.
+\end{definition}
+We say that forecaster $w$ wins the competition if $M(y, x) = w$.
+We call a forecaster selection mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts.
 
-We call a forecaster selection mechanism truthful iff, for all forecasters, their probability of winning is maximized when they reports their beliefs as their forecasts.\\
-
-\textbf{Definition 2: Truthful:}\\
-$M$ is truthful iff $\forall i \in [n]$, $\forall \hat{\theta}_i$, $\forall y^{\prime}_i \neq \hat{\theta}_i$, and $\forall y_j s.t. j \neq i$,
+\begin{definition}
+  \label{truthfullness}
+  $M$ is \textbf{truthful} iff $\forall i \in [n]$, $\forall \hat{\theta}_i$, $\forall y^{\prime}_i \neq \hat{\theta}_i$, and $\forall y_j s.t. j \neq i$,
 \[ P(M( (y_1, ..., \hat \theta_i, .., y_n), x ) = i) \geq  P(M( (y_1, ..., \hat y_i, .., y_n), x ) = i)\]
-\textbf{Note:} $M$ is strictly truthful if the strict inequality inequality holds.\\
+$M$ is \textbf{strictly truthful} if the strict inequality inequality holds.
+\end{definition}
 
 Additionally, we would like our mechanism to choose the forecaster with the best predictions.
-We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities.\\
+We define the accuracy of a single forecaster $i$ as 1 minus the average squared loss of their forecasts compared to the true probabilities.
 
-\textbf{Definition 3: Accuracy:}\\
-$a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$.\\
+\begin{definition}
+  \label{accuracy}
+  A forecaster's \textbf{accuracy} is $a_i = 1 - \frac{1}{m}\sum_{k=1}^m (y_{i, k} - \theta_k)^2$.
+\end{definition}
+An ideal mechanism would choose forecasters with larger accuracies with higher probabilities. Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$.
 
-An ideal mechanism would choose forecasters with larger accuracies with higher probabilities. Let $i^* = \argmax_i a_i$ be the highest accuracy forecaster, and let $a^* = a_{i^*}$.\\
+\begin{definition}
+  \label{accuracy_gap}
+  The \textbf{accuracy gap} $\epsilon = a^* - \max_{i \neq i^*} a_i$ is the difference in accuracy of the first and second best forecasters.
+\end{definition}
 
-\textbf{Definition 4: Accuracy Gap:}\\
-$\epsilon = a^* - \max_{i \neq i^*} a_i$ denote the accuracy gap.\\
-
-For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$.
+% For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$.
 Specifically, for any $m > m_\delta(M, n, \epsilon)$, $P(M(y, x) \neq i^*) \leq \delta$.
 $m_\delta$ gives us a measure of how many events are needed for a mechanism to stably pick the best forecaster.
-We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.\\
+We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.
 
-Similar to work in \cite{elf}, we will focus on using the \textbf{proper scoring rule}, the \textbf{quadratic scoring rule} in our forecaster selection mechanism.\\
+Similar to work in \cite{elf}, we will focus on using the proper scoring rule, the quadratic scoring rule in our forecaster selection mechanism.
 
-\textbf{Definition 5: Proper Scoring Rule}:\\
-Scoring rule, $R$ is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$\\
+\begin{definition}
+  \label{scoring_rule}
+  A \textbf{scoring rule}, $R$ is proper if $\forall p,y \in {0,1}, E_{x~p}[R(p,x)] \ge E_{x~p}[R(y,x)]$
+\end{definition}
 
-\textbf{Definition 6: Quadratic Scoring Rule}:\\
-$R_q = 1 - (y - x)^2$; Where $x$ denotes the observed outcome, and $y$ denotes the report.
+\begin{definition}
+  \label{quadratic_scoring_rule}
+  The \textbf{quadratic scoring rule}, is $R_q = 1 - (y - x)^2$, where $x$ denotes the observed outcome, and $y$ denotes the report.
+\end{definition}
 
@@
 \subsection{Truthfulness}
-show simple counterexample(s?) \\
-- single event favors extremes \\
-- multiple events can be dominated by single untruthful event when rest are isomorphic \\
+This mechanism is not truthful, as we can see with a few counterexamples.
+First, consider the case of a single event with $\theta = 0.9$, with $n = 2$.
+If both forecasters correctly report $0.9$, they will each with with probability $\frac{1}{2}$.
+However, if either of them deviates and reports some $y > 0.9$, they will win whenever $x = 1$.
+This happens with probability 0.9, so it increases their probability of winning.
+Therefore, this is an advantageous misreport, so $M_s$ is not truthful.
+
+This extends to multiple events as well.
+If event 1 is the event given above, and for every subsequent event both forecasters report the same $y$, their overall score will be the same for all events but the first one, so that will determine the winner.
+Therefore, the untruthful forecaster will still have an advantage, so $M_s$ is not truthful for multiple events either.
 
@@
   Given random variables $X_i$ for $1 \leq i \leq n$ such that $0 \leq X_i \leq 1$ almost surely, let $S = \sum_i X_i$. Then,
-  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } \]
+  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } ~.\]
 \end{theorem}
@@
   \label{elf_bound}
-    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$
+    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$ ~.
     % For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
@@
   \label{elf_lower_bound}
-    For $\delta < \frac{1}{2}$, $m_\delta(\elf, n, \epsilon) > n \log n$
+    For $\delta < \frac{1}{2}$, $m_\delta(\elf, n, \epsilon) > n \log n$.
 \end{theorem}
@@
 \end{theorem}
-\emph{Proof:} For each forecaster $j \in [1, n]$ fix forcaster's report.
+\emph{Proof:} For each forecaster $j \in [1, n]$ fix forecaster's report.
 
@@
   \label{shelf_bound}
-    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$
+    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$.
 \end{theorem}

### 2020-11-20 paper/draft1.tex
Update draft1.tex

@@
 
-S'pose that for some forecaster $i$, $i$'s report on some subset of events, where $k \in [1, m]$ denotes the size of this subset, does not maximize their expected score for any of those individual events.\\
+Suppose that for some forecaster $i$, $i$'s report on some subset of events, where $k \in [1, m]$ denotes the size of this subset, does not report their true belief for any of the $k$ events.\\
 Let $k^\prime$ be one of those events.
 
-We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to maximize their expected score on each $k$ events.
+We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to report their true belief on each of the $k$ events.
 A guiding intuition here would be as follows: The higher the expected score a forecaster has on a given event, the higher the probability that SHELF awards them a point on this specific event, and the only way to maximize one's probability of being selected as the best forecaster is to increase the number of points they are awarded.
 Therefore, for a single independent event, increasing one's expected score will either increase the probability of being selected as the best forecaster or leave it unchanged, and it does so without altering results of any other event.
-In this way, we will show that being truthful for a singular event will always increase one's probability of being selected as the best forecaster.
+In this way, we will show that being truthful for a singular event will always increase one's probability of being selected as the best forecaster, because, using a quadratic scoring rule, a forecaster's expected score is maximized when reporting their true belief.
 We can then repeat this process for each untruthful report to maximize the probability of being selected as the best forecaster.\\\\
@@
     $$\forall j \in [1,m] \text{ s.t. } j \ne i; V(i) - V(j) \geq 2$$
-    For this case, $i$'s probability of being selected as the best forecaster is either $1$ or $0$.
+    For this case, $i$'s probability of being selected as the best forecaster is either exactly $1$ or $0$.
 It is also unaffected by being truthful or not in $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.
@@
     In any given configuration, a forecaster's probability of being selected as the best forecaster is maximized when the minimal number of other forecaster have as many points as them.
-In the SHELF mechanism, any forecaster's probability of scoring a point on a given event is independent of all other.
+In the SHELF mechanism, any forecaster's probability of scoring a point on a given event is independent of all others.
 Therefore, there is no action that can be taken to minimize the probability of any competitor's probability of being selected as the best forecaster except strictly increasing one's own point total.

### 2020-11-24 paper/draft1.tex
bo's changes

@@
 
-\usepackage[margin=1.5in]{geometry}
+%\usepackage[margin=1.5in]{geometry}
+\usepackage{fullpage}
 \usepackage{amssymb}
@@
 \usepackage{bbm}
+\usepackage{amsthm}
+\usepackage[authoryear]{natbib}
+
 \usepackage{mathrsfs}
@@
 
-% \title{ELF}
-% \author{Anish Thilagar}
-% \date{\today}
-% \maketitle
+\title{Efficient and Truthful Forecasting Competitions}
+\author{Rafael Frongillo, Robert Gomez, Anish Thilagar, Bo Waggoner}
+\date{\today}
+\maketitle
 
-% \begin{abstract}
+\begin{abstract}
+   \citet{witkowski2018incentive} studied competitions among forecasters who predict a set of common events.
+   When such a competition picks a single winner, incentives can be distorted, so that paper introduced the ELF mechanism which incentivizes truthful forecasts.
+   In this paper, we give a tighter analysis of the ELF mechanism, then give a mechanism that improves upon it exponentially, in the sense of also being truthful but requiring only logarithmically many events in order to select the best forecaster with high probability.
+   These results have potential applications to machine-learning competitions such as Kaggle, where winners are currently selected in non-truthful ways. 
+\end{abstract}
 
-% \end{abstract}
-\section{Name???}
+\section{Introduction}
 - SHELF\\
@@
   \label{mechanism}
-  A \textbf{selection mechanism} $M(y, x)$ is a map from the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_m)$ to an index $w \in [1, n]$.
+  A \textbf{selection mechanism} $M(y, x)$ is a map from the forecasts $y = (y_1, ..., y_n)$ and outcomes of the events $x = (x_1, ..., x_k)$ to an index $w \in [1, n]$.
 \end{definition}
@@
 
-% For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$.
+For a given mechanism $M$ and $n$ forecasters with accuracy gap $\epsilon$, we let $m_\delta$ be the minimum number of events such that $M$ necessarily chooses $i^*$ with probability at least $1 - \delta$.
 Specifically, for any $m > m_\delta(M, n, \epsilon)$, $P(M(y, x) \neq i^*) \leq \delta$.
-$m_\delta$ gives us a measure of how many events are needed for a mechanism to stably pick the best forecaster.
+$m_\delta$ gives us a measure of how many events are needed for a mechanism to pick the best forecaster.
 We will use it as a metric to compare mechanisms, where we say $M$ is more efficient than $M'$ if $m_\delta(M, n, \epsilon) < m_\delta(M', n, \epsilon)$, since $M$ needs less events to consistently pick the best forecaster.
 
-Similar to work in \cite{elf}, we will focus on using the proper scoring rule, the quadratic scoring rule in our forecaster selection mechanism.
+Similar to work in \cite{witkowski2018incentive}, we will focus on using the proper scoring rule, the quadratic scoring rule in our forecaster selection mechanism.
 
@@
 
+\subsection{Useful facts}
+Bo: TODO name this subsection better.
+
+The following facts, easy to derive and used by \citet{witkowski2018incentive}, will be useful to us as well.
+
+\begin{lemma} \label{lemma:score-accuracy}
+  The expected score, from the ground truth point of view, of forecaster $i$ on event $k$ is $1 - \theta_k(1-\theta_k) - (y_{i,k} - \theta_k)^2$.
+\end{lemma}
+\begin{proof}
+By definition, the expected score is
+\begin{align*}
+  &\theta_k \left[1 - (1 - y_{i,k})^2\right] + (1 - \theta_k) \left[1 - y_{i,k}^2\right]  \\
+  &= \theta_k \left[2y_{i,k} - y_{i,k}^2\right] + (1-\theta_k)\left[1 - y_{i,k}^2\right]  \\
+  &= 1 - \theta_k + 2 \theta_k y_{i,k} - y_{i,k}^2  \\
+  &= 1 - \theta_k + \theta_k^2 - (y_{i,k} - \theta_k)^2 .
+\end{align*}
+\end{proof}
+
+Averaging over events, we get that $i$'s score on average over the $m$ events, in expectation, is exactly her accuracy minus some penalty term that only depends on how extreme the ground truth events are.
+\begin{corollary} \label{cor:avg-score-accuracy}
+  The expectation of forecaster $i$'s average score on all events, from the ground truth point of view, is $a_i - \frac{1}{m}\sum_{k=1}^m \theta_k (1 - \theta_k)$, where $a_i$ is $i$'s accuracy.
+\end{corollary}
+
+We also immediately obtain:
+\begin{corollary} \label{cor:diff-score-accuracy}
+  The expected difference in average scores of forecaster $i$ and $j$, from a ground truth point of view, is $a_i - a_j$.
+\end{corollary}
+
 \section{Simple average mechanism}
-A simple selection mechanism that is often done in practice, we will call the simple average mechanism $M_s$.
+A straightforward selection mechanism often used in practice is what we call the \emph{simple average mechanism} $M_s$.
 For this mechanism, we assign each forecaster a score $f_{i, k} = R_q(y_{i, k}, x_k)$ for each event.
@@
 Finally, we choose the forecaster with the highest cumulative score $M_s(y, x) = \argmax_i F_i$.
-The idea of this mechanism is that each forecaster's final score in this mechanism is $F_i = \sum_{i=1}^m 1 - (y_{i, j} - x_i)^2$ is an analog for their cumulative accuracy, $m a_i = \sum_{k=1}^m 1 - (y_{i, k} - \theta_k)^2$.
+
+%%%% Bo: this is good, but I thought we don't need this detail.
+%The idea of this mechanism is that each forecaster's final score in this mechanism is $F_i = \sum_{i=1}^m 1 - (y_{i, j} - x_i)^2$ is an analog for their cumulative accuracy, $m a_i = \sum_{k=1}^m 1 - (y_{i, k} - \theta_k)^2$.
 Therefore, the forecaster with the highest score will correlate to the forecaster with the highest accuracy.
@@
 \subsection{Truthfulness}
-This mechanism is not truthful, as we can see with a few counterexamples.
-First, consider the case of a single event with $\theta = 0.9$, with $n = 2$.
-If both forecasters correctly report $0.9$, they will each with with probability $\frac{1}{2}$.
-However, if either of them deviates and reports some $y > 0.9$, they will win whenever $x = 1$.
-This happens with probability 0.9, so it increases their probability of winning.
-Therefore, this is an advantageous misreport, so $M_s$ is not truthful.
 
-This extends to multiple events as well.
-If event 1 is the event given above, and for every subsequent event both forecasters report the same $y$, their overall score will be the same for all events but the first one, so that will determine the winner.
-Therefore, the untruthful forecaster will still have an advantage, so $M_s$ is not truthful for multiple events either.
+%show simple counterexample(s?) \\
+%- single event favors extremes \\
+%- multiple events can be dominated by single untruthful event when rest are isomorphic \\
 
-\subsection{Accuracy}
-Even though $M_s$ is not truthful, we assume that forecasters still report their true beliefs $\hat \theta_i$.
-For a single event, the most extreme forecasters will always get selected.
-For example, if the single outcome is $x = 0$, the forecaster with the minimum $\hat \theta_i $ will have the highest score, so they will always win.
-Similarly if $x = 1$, the highest belief forecaster will always win.
+As observed by \citet{witkowski2018incentive} and discussed in depth by \citet{lichtendahl2007probability}, this mechanism is generally not truthful.
+We can consider a simple example with three forecasters and one event, whose true probability is $0.5$.
+Alice predicts $0.5$, but Bob predicts $1$ and Charlie predicts $0$.
+Observe that Alice \emph{cannot win}, despite being the best forecaster by far: either the event occurs (Bob wins) or it doesn't (Charlie wins).
+She can only win be predicting either $0$ or $1$, raising her probability of winning from $0$ to $0.25$, assuming a random tiebreaking rule.
 
-However, for multiple events, the averaging starts to favor more forecasters.
-We will see that we get a similar $m_\delta$ as the SHELF mechanism introduced later, assuming the forecasters remain truthful.
-In fact, the main advantage of SHELF is that it is as efficient as $M_s$ while also being truthful.
+\subsection{Efficiency}
+Although the simple average mechanism is not truthful, it is worth studying its efficiency because, intuitively, it seems unlikely to do better using a mechanism that relies on the quadratic scores of the participants.
+So as a benchmark for truthful quadratic-score-based mechanisms, let us consider the efficiency of $M_s$ if forecasters were to report their true beliefs $\hat \theta_i$.
+
+For a single event, the most extreme forecasters will always get selected, as in the example above.
+However, for multiple events, the averaging starts to favor more accurate forecasters.
+In fact, one can show that with $n$ forecasters and an accuracy gap of $\epsilon$, only
+
+  \[ m = \frac{2}{\epsilon^2}\ln\left(\frac{n}{\delta}\right) \]
+events suffice to select the best forecaster with probability $1-\delta$.
+
+Sketch (similar to the \citet{witkowski2018incentive} analysis of ELF): Let $i$ be the best forecaster.
+She beats some competitor $j$ if she has a higher average score in the competition.
+The expected difference in average scores is the difference in accuracies (Corollary \ref{cor:diff-score-accuracy}), which is $a_i - a_j \geq \epsilon$.
+On any given event, the difference in scores is an independent random variable bounded in $[-1,1]$.
+A standard Hoeffding bound \cite{Bo:todo-cite-or-reference}  shows that the average of $m = \frac{2}{\epsilon^2}\ln\tfrac{n}{\delta}$ such variables is at least $\epsilon$ below its mean with probability $1 - \tfrac{\delta}{n}$.
+Complete the argument by taking a union bound over all $n-1 \leq n$ opponents $j$.
+
+This shows that it is possible to select the best forecaster using a number of events only logarithmic in $n$, the number of forecasters -- if truthfulness is not required.
+We next consider the number of events used by the ELF mechanism.
 
@@
 \newcommand{\elf}{M_{\mathrm{ELF}}}
-The ELF mechanism $\elf$ \cite{elf}, improves upon $M_s$, by incentivizing forecasters to be truthful.
+The ELF mechanism $\elf$ \citep{witkowski2018incentive}, improves upon $M_s$, by incentivizing forecasters to be truthful.
 For each event $k$, we hold a lottery to choose a winner.
@@
 
-In Theorem 6 of \cite{elf}, it is proven that $\elf$ is strictly truthful. In Theorem 8 of the same paper, they also upper bound $m_\delta$ by showing 
+In Theorem 6 of \cite{witkowski2018incentive}, it is proven that $\elf$ is strictly truthful. In Theorem 8 of the same paper, they also upper bound $m_\delta$ by showing 
 \[ m_\delta(\elf, n, \epsilon) \leq \frac{2(n-1)^2}{\epsilon^2} \ln \left(\frac{4(n-1)}{\delta}\right)\]
@@
 Then, $F_i = \sum_k F_{i, k}$ is the random variable that is the number of events forecaster $i$ wins.
-The proof of Theorem 8 \cite{elf} utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance.
+The proof of Theorem 8 \cite{witkowski2018incentive} utilized the Hoeffding bound applied to $F_i$, which assumes they have high variance.
 However, this is not the case, and utilizing that fact gives an improvement in the lower bound.
@@
   Given random variables $X_i$ for $1 \leq i \leq n$ such that $0 \leq X_i \leq 1$ almost surely, let $S = \sum_i X_i$. Then,
-  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } ~.\]
+  \[ P\left(|S - \E[S]| < t\right) < 2 \: e^{\frac{-t^2 }{2\left(\Var(S) + \frac{t}{3}\right)} } \]
 \end{theorem}
@@
   \label{elf_bound}
-    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$ ~.
+    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$
     % For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
@@
 
-Since $F_i = \sum_k F_{i, k}$, we have $\Var(F_i) = \sum_k \Var(F_{i, k}) < \sum_k \frac{2}{n} = \frac{2m}{n}$. As shown in [elf paper], for $j\neq i$ we have 
+Since $F_i = \sum_k F_{i, k}$, we have $\Var(F_i) = \sum_k \Var(F_{i, k}) < \sum_k \frac{2}{n} = \frac{2m}{n}$. As shown in \citet{witkowski2018incentive}, for $j\neq i$ we have 
 \[ \E[F_i] - \E[F_j] \geq \frac{m \epsilon}{n - 1}\]
@@
   \label{elf_lower_bound}
-    For $\delta < \frac{1}{2}$, $m_\delta(\elf, n, \epsilon) > n \log n$.
+    For $\delta < \frac{1}{2}$, $m_\delta(\elf, n, \epsilon) > n \log n$
 \end{theorem}
@@
 \emph{Proof:}
-From Theorem 1 of \cite{bnb}, we know that for $m = n \log n$, $P(M > k_\alpha) = 1 - o(1) > C_2$ for some constant $C_2$, where $c = \frac{m}{n\log n}$, $k_\alpha = (d_c - 1 + \alpha) \log n$, and $0 < 1 < \alpha$, such that $d_c$ is the larger solution of $1 + x(\log c - \log x + 1) - c= 0$.
+From Theorem 1 of \citet{raab1998balls}, we know that for $m = n \log n$, $P(M > k_\alpha) = 1 - o(1) > C_2$ for some constant $C_2$, where $c = \frac{m}{n\log n}$, $k_\alpha = (d_c - 1 + \alpha) \log n$, and $0 < 1 < \alpha$, such that $d_c$ is the larger solution of $1 + x(\log c - \log x + 1) - c= 0$.
 
@@
 \subsection{Truthfulness}
-Note: The following analysis is inspired by and follows the work done in \cite{elf}.\\\\
+Note: The following analysis is inspired by and follows the work done in \citet{witkowski2018incentive}.
+
+(This is wrong because we can't just look at their probability of winning a point. We need to also factor in the tiebreaker weighting some wins differently)
+
 For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events.
@@
 This is maximized when $y_i = \theta$, so the mechanism is truthful.
-(what theorem 4 does) We can also see this directly be noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.
+We can also see this directly by noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.
 
@@
 \end{theorem}
-\emph{Proof:} For each forecaster $j \in [1, n]$ fix forecaster's report.
+\emph{Proof:} For each forecaster $j \in [1, n]$ fix their report.
 
@@
 
-% From Proposition 2 of \cite{elf}, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$.
+% From Proposition 2 of \citet{witkowski2018incentive}, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$.
 Additionally, for a single event, a forecaster's accuracy $a_i$ is by definition just $R_q(y, \theta)$.
@@
   \label{shelf_bound}
-    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$.
+    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$
 \end{theorem}
-\emph{Proof:} This proof is a slight modification of the proof of Theorem 8 in \cite{elf}.
+\emph{Proof:} This proof is a slight modification of the proof of Theorem 8 in \cite{witkowski2018incentive}.
 
@@
 
-\begin{thebibliography}{99}
-\bibitem{elf} Witkowski, Freeman  \emph{Incentive-Compatible Forecasting Competitions} \url{https://las.inf.ethz.ch/files/witkowski-etal-aaai2018.pdf}.
+\bibliographystyle{plainnat}
+\bibliography{references}
 
-\bibitem{bnb} Raab, Steger  \emph{“Balls into Bins” — A Simple and Tight Analysis} \url{http://www.dblab.ntua.gr/~gtsat/collection/scheduling/Balls%20into%20Bins%20A%20Simple%20and%20Tight%20Anal.pdf}.
-
-\end{thebibliography}
+%\begin{thebibliography}{99}
+%\bibitem{elf} Witkowski, Freeman  \emph{Incentive-Compatible Forecasting Competitions} \url{https://las.inf.ethz.ch/files/witkowski-etal-aaai2018.pdf}.
+%
+%\bibitem{bnb} Raab, Steger  \emph{“Balls into Bins” — A Simple and Tight Analysis} \url{http://www.dblab.ntua.gr/~gtsat/collection/scheduling/Balls%20into%20Bins%20A%20Simple%20and%20Tight%20Anal.pdf}.
+%\end{thebibliography}
 

### 2020-11-24 paper/draft1.tex
m_delta proof for any m = cn log n

@@
 \end{theorem}
-\emph{Proof:} Pick some $\delta < \frac{1}{2}$ and consider the case where $m = n \log n$ and $\theta_k = 1$ for every event.
+\emph{Proof:} Pick any $\delta < \frac{1}{2}$, $0 < c \leq 1$ and consider the case where $m = c n \log n$ and $\theta_k = 1$ for every event.
 Let $y_{1, k} = 1$ and $y_{i, k} = 0$ for every $i > 1$.
@@
 
-Since all the events are uniform, the expected number of lotteries forecaster 1 will win is $m f_1 = \frac{2m}{n} = 2 \log n$.
-Specifically, their wins will follow the Bernoulli distribution $B(n, \frac{2}{n})$.
-With some probability $C_1 = P(B(n, \frac{2}{n}) < 2\log n) \approx \frac{1}{2}$, forecaster 1 will win less events than expected.
+Since all the events are uniform, the expected number of lotteries forecaster 1 will win is $m f_1 = \frac{2m}{n} = 2 c \log n$.
+Specifically, their wins will follow the Bernoulli distribution $B(m, \frac{2}{n})$.
+With some probability $C_1 = P(B(m, \frac{2}{n}) < 2 c \log n) \approx \frac{1}{2}$, forecaster 1 will win less events than expected.
 
@@
 \begin{lemma}
-    $P(M > 2 \log n) = 1 - o(1)$.
+    $P(M > 2 c \log n) = 1 - o(1)$ for any $0 < c \leq 1$.
 \end{lemma}
 \emph{Proof:}
-From Theorem 1 of \citet{raab1998balls}, we know that for $m = n \log n$, $P(M > k_\alpha) = 1 - o(1) > C_2$ for some constant $C_2$, where $c = \frac{m}{n\log n}$, $k_\alpha = (d_c - 1 + \alpha) \log n$, and $0 < 1 < \alpha$, such that $d_c$ is the larger solution of $1 + x(\log c - \log x + 1) - c= 0$.
+From Theorem 1 of \citet{raab1998balls}, we know that for $m = c n \log n$, $P(M > k_\alpha) = 1 - o(1)$, where $k_\alpha = (d_c - 1 + \alpha) \log n$, and $0 < 1 < \alpha$, such that $d_c$ is the solution of $1 + x(\log c - \log x + 1) - c= 0$ such that $x > c$.
 
-In our case, $c = 1$, so $d_c$ is the solution to $x (1 - \log x) = 0$.
-Therefore, $d_c = e$.
+If $c = 1$, this reduces to $d_1 (1 - \log d_1) = 0$, so $d_1 = e$.
 Since this inequality holds for any $\alpha$, we let $\alpha = 3 - e$.
 Plugging in both values gives us $k_\alpha = 2 \log n$, so $P(M > 2 \log n) = 1 - o(1)$.
-\hfill \QED
 
-Using the lemma, for any $C_2 < 1$ and sufficiently large $n$, $P(M > 2 \log n) > C_2$. We choose some $C_2 > 2\delta$. Now, the probability that forecaster 1 is not chosen is at least
+We can then rewrite the equation that determines $d_c$ as $1 + \frac{1}{x} = \frac{c}{x} - \log \frac{c}{x} $.
+$\frac{d}{dx}$ of the left hand side is $-\frac{1}{x^2} < 0$ while the right hand side is $\frac{x-c}{x^2} > 0$, since we are only considering the solution where $x > c$.
+For any $c < 1$, $x = ce$ will not satisfy the equation, since the right hand side remains constant while the left is increasing from our $d_1$ solution.
+In order for the left side to decrease and the right side to increase, $x$ must increase.
+Therefore, $d_c > ce$ for $0 < c < 1$.
+
+Letting $\alpha = \max (c (2-e) + 1, 0)$, we have
 \[
-  P(B(n, \frac{2}{n}) < 2\log n) \times P(M > 2 \log n) > \frac{1}{2} \times 2\delta = \delta
+k_\alpha = (d_c - 1 + \alpha) \log n > (ce - 1 + c (2-e) + 1) \log n = 2c \log n \:.
 \]
-Therefore, it is not true that for any $n$, $\epsilon$, $P(\elf(y, x) \neq i^*) \leq \delta$ when $m = n \log n$. Therefore, $m_\delta(\elf, n, \epsilon) > n \log n$. 
+We can again apply Theorem 1 of \citet{raab1998balls} to get
+\[
+P(M > 2 c \log n) > P(M > k_\alpha) = 1 - o(1)
+\]
+for any $c < 1$. Therefore, for any $c \leq 1$, $P(M > 2 c \log n) = 1 - o(1)$. \hfill \QED
+
+Using the lemma, for any $C_2 < 1$ and sufficiently large $n$, $P(M > 2 c \log n) > C_2$. We choose some $C_2 > 2\delta$. Now, the probability that forecaster 1 is not chosen is at least
+\[
+  P\left(B\left(m, \frac{2}{n}\right) < 2c \log n\right) \times P(M > 2 c \log n) > \frac{1}{2} \times 2\delta = \delta
+\]
+Therefore, it is not true that for any $n$, $\epsilon$, $P(\elf(y, x) \neq i^*) \leq \delta$ when $m = c n \log n$. Therefore, $m_\delta(\elf, n, \epsilon) \neq c n \log n$ for any $c < 1$.
+
+Therefore, $m_\delta(\elf, n, \epsilon) > n \log n$. 
 \hfill \QED

### 2021-01-12 paper/draft1.tex
latest version from overleaf

@@
 \newcommand*{\QED}{\hfill\ensuremath{\square}}%
+
+\newcommand{\elf}{M_{\mathrm{ELF}}}
+\newcommand{\shelf}{M_{\mathrm{SHELF}}}
 
@@
 \section{ELF}
-\newcommand{\elf}{M_{\mathrm{ELF}}}
 The ELF mechanism $\elf$ \citep{witkowski2018incentive}, improves upon $M_s$, by incentivizing forecasters to be truthful.
@@
 \section{SHELF}
-\newcommand{\shelf}{M_{\mathrm{SHELF}}}
 
@@
 
+\newpage
+\section{Raf notes}
+
+Let's study the one-round version of ELF + SHELF + noise.
+And actually, we won't really need to use SHELF per se.
+Let's actually define
+$M_{f,\sigma}(y,x) = \max_{i\in[n]} f(y,x)_i + X_i$ where the $X_i \sim N(0,\sigma^2)$ are indpendent, and $f$ is any function with $f(y,x) \in [0,m]^n$ where if you change only one entry of $y$ by $c$, then $f$ changes by at most $c^2$.
+(For example, $f$ could be the sum of scores.)
+Let $M_\alpha$ be the mechanism that runs $M_{f,\sigma}$ with probability $\alpha$ and $\elf$ with probability $1-\alpha$.
+
+In what follows, when I omit $x$, I'm implicitly taking the randomness over $x$ into account (from $\theta$).
+Assume $y$ is truthful for forecaster $i$ and $y'$ is any vector that differs only in $i$'s forecast on a particular round.
+And actually let's focus on the case $m=1$, so there is only one round anyway.
+From a direct calculation (see also a Prop.\ in \cite{witkowski2018incentive}), we have, from forecaster $i$'s point of view,
+\begin{align}
+  \Pr[\elf(y)=i] - \Pr[\elf(y')=i] = \tfrac 1 n (y_i - y'_i)^2~,
+\end{align}
+since forecaster $i$ believes $y_i = \theta_1$.
+
+By differential privacy (I have not checked this carefully!), and the fact that $\exp(c) \leq 1+2c$ for $c\in[0,1]$, we have, for each $x$,
+\begin{align}
+  \Pr[M_{f,\sigma}(y',x)=i]
+  & \leq \exp\left( \frac{(y_i-y'_i)^2}{2\sigma^2} \right) \Pr[M_{f,\sigma}(y,x)=i]
+  \\
+  & \leq \left(1 + \frac{(y_i-y'_i)^2}{\sigma^2}\right) \Pr[M_{f,\sigma}(y,x)=i]
+  \\
+  & \leq \Pr[M_{f,\sigma}(y,x)=i] + \frac{(y_i-y'_i)^2}{\sigma^2}~.
+\end{align}
+
+Combining, the probability of $i$ winning for $y$ and $y'$ can be compared as follows.
+\begin{align}
+  &\Pr[M_\alpha(y)=i]-\Pr[M_\alpha(y')=i]\\
+  &=\alpha\left(\Pr[M_{f,\sigma}(y)=i] - \Pr[M_{f,\sigma}(y')=i]\right)\\
+  &\qquad + (1-\alpha)\left(\Pr[\elf(y)=i] - \Pr[\elf(y')=i]\right)~.
+  \\
+  &\geq -\alpha \frac{(y_i-y'_i)^2}{\sigma^2} + (1-\alpha) \frac{(y_i-y'_i)^2}{n}
+  \\
+  &\geq \left((1-\alpha) \frac{1}{n} -\alpha \frac{1}{\sigma^2}\right) (y_i-y'_i)^2~.
+\end{align}
+Thus, setting $\sigma^2 = n \tfrac \alpha {1-\alpha}$ gives truthfulness, e.g.\ $\sigma^2=n$ for $\alpha=\tfrac 1 2$.
+Which is maybe not what we were hoping for, but it's something.
+
 \bibliographystyle{plainnat}
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2021-01-12 paper/draft2.tex
new draft

--- 2020-11-24 paper/draft1.tex
@@
 
+\newcommand{\elf}{M_{\mathrm{ELF}}}
+\newcommand{\shelf}{M_{\mathrm{SHELF}}}
+
 \newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
@@
 \section{Introduction}
-- SHELF\\
-- GNOME\\
-- ???
-
-keywords: event, forecast, voting
-
-EFV
 
@@
   \label{elf_bound}
-    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$
+    $m_\delta(\elf, n, \epsilon) \leq \frac{5(n-1)}{\epsilon^2}\ln\left(\frac{4(n-1)}{\delta}\right)$.
     % For an accuracy gap $\epsilon$, ELF correctly chooses the most accurate forecaster with probability at least $1 - 4 (n-1) e^{-\frac{m \epsilon}{6(n - 1)}}$.
@@
 
-\section{SHELF}
-\newcommand{\shelf}{M_{\mathrm{SHELF}}}
+\subsection{Other point-per-round mechanisms}
+We can extend Theorem \ref{elf_lower_bound} to apply to any normal, anonymous mechanism that assigns a single point per event to 1 forecaster, and then picks the forecaster with the highest score.
+We can treat such a forecaster selection mechanism as a budget-balanced wagering mechanism for each event, where each forecaster has a shared, fixed wager of $\frac{1}{n}$.
+Since we want the mechanism to by symmetric, we can assume it satisfies anonymity as described in [wagering mechanism paper].
 
-For this mechanism, we let the binary random variable $X_{i, k}$ be 1 with probability $R_q(y_{i, k}, x_i)$, and 0 otherwise.
-Then, for each event $k$ we assign forecaster $i$ the score $f_{i, k} = X_{i, k}$ obtained by sampling this variable.
-Finally, we assign their final score by summing these over all events, $F_i = \sum_{j=1}^m f_{i, j}$, then chose the forecaster with the highest score $\shelf(y, x) = \argmax_i F_i$, breaking ties uniformly at random.
+(TODO: justify normality).
 
-\subsection{Truthfulness}
-Note: The following analysis is inspired by and follows the work done in \citet{witkowski2018incentive}.
-
-(This is wrong because we can't just look at their probability of winning a point. We need to also factor in the tiebreaker weighting some wins differently)
-
-For a single event with true probability $\theta$, every forecaster will either win 1 or 0 events.
-The probability that their final score is 1 will just be their expected score for the single event.
-Therefore, to maximize their final score, each forecaster must maximize their expected score for the single event.
-Their score is just $\E_{x \sim \theta}(R_q(y_i, x)) = \E_{x \sim \theta}(1 - (y_i - x)^2)$.
-This is maximized when $y_i = \theta$, so the mechanism is truthful.
-We can also see this directly by noting that $R_q$ is a strictly proper scoring rule, so its expectation is maximized when $y_i = \theta$.
-
-\begin{theorem}
-  \label{shelf_truthful}
-    $\shelf$ is truthful for $m \geq 1$ events.
-\end{theorem}
-\emph{Proof:} For each forecaster $j \in [1, n]$ fix their report.
-
-Suppose that for some forecaster $i$, $i$'s report on some subset of events, where $k \in [1, m]$ denotes the size of this subset, does not report their true belief for any of the $k$ events.\\
-Let $k^\prime$ be one of those events.
-
-We will now show that $i$ will maximize their probability of being chosen as the best forecaster in the SHELF mechanism iff they alter their $k$ reports to report their true belief on each of the $k$ events.
-A guiding intuition here would be as follows: The higher the expected score a forecaster has on a given event, the higher the probability that SHELF awards them a point on this specific event, and the only way to maximize one's probability of being selected as the best forecaster is to increase the number of points they are awarded.
-Therefore, for a single independent event, increasing one's expected score will either increase the probability of being selected as the best forecaster or leave it unchanged, and it does so without altering results of any other event.
-In this way, we will show that being truthful for a singular event will always increase one's probability of being selected as the best forecaster, because, using a quadratic scoring rule, a forecaster's expected score is maximized when reporting their true belief.
-We can then repeat this process for each untruthful report to maximize the probability of being selected as the best forecaster.\\\\
-Formally, we will analyze three cases relating to the context provided by the $m - 1$ events other than $k^\prime$.
-
-Let $V(i)$ denote the number of points forecaster $i$ has accrued.\\
-Let $f_{i,k}$ denote the probability forecaster $i$ scores a point on event $k$.\\
-
-\begin{enumerate}
-    \item Some forecaster $j$ scores at least two more points than $i$, OR $i$ scores at least two more points than any other forecaster.\\
-    $$\exists j \in [1,m] \text{ s.t. } j \ne i \text{ and } V(j) - V(i) \geq 2$$ 
-    $$OR$$
-    $$\forall j \in [1,m] \text{ s.t. } j \ne i; V(i) - V(j) \geq 2$$
-    For this case, $i$'s probability of being selected as the best forecaster is either exactly $1$ or $0$.
-It is also unaffected by being truthful or not in $k^\prime$, because gaining, or failing to gain, $1$ point in this context is not enough to alter the outcome as only the forecaster with the most number of points is chosen as the best forecaster with ties broken uniformly.
-
-    \item Some forecaster $j$ scores exactly one more point than $i$, AND no other forecasters score strictly more points than $i$.\\
-    $$\exists j \in [1,m] \text{ s.t. } j \neq i \text{ and } V(j) - V(i) = 1$$
-    $$AND$$
-    $$\forall l \in [1,m] \text{ s.t. } l \neq i \text{ and } l \neq j; V(i) - V(l) \geq 0$$
-    For this case, $i$ must seek to maximize $f_{i,k^\prime}$ to have any non-zero probability of being selected as the best forecaster under the SHELF mechanism. 
-    In the SHELF mechanism, the maximum payout a forecaster can receive for a single event is $1$, and that point is awarded to them with probability exactly equal to their quadratic score.
-Thus, we know a forecaster's expected value for a singular event is exactly their quadratic score.
-Since the quadratic scoring rule is proper, we know that the expectation of a forecaster's quadratic score is maximized when the forecaster is reporting their true beliefs.
-As a result, we can conclude that the only way for $i$ to maximize their probability of receiving a point in $k^\prime$ is to report their true beliefs.
-By reporting their true beliefs, which maximizes the probability that they score another point, $i$ also maximizes the probability of being selected as the best forecaster which, in this context, occurs when only $i$ scores a point and the tie between $j$ and $i$ is broken uniformly via the rules of SHELF.
-
-    \item No forecasters score more points than $i$, but there is at least one forecaster $j$ that scores the same number of points as $i$ or scores exactly one less point than $y_i$.
-    $$\exists j \in [1,m] \text{ s.t. } j \ne i \text{ and } V(i) - V(j) \in \{0,1\}$$
-    In any given configuration, a forecaster's probability of being selected as the best forecaster is maximized when the minimal number of other forecaster have as many points as them.
-In the SHELF mechanism, any forecaster's probability of scoring a point on a given event is independent of all others.
-Therefore, there is no action that can be taken to minimize the probability of any competitor's probability of being selected as the best forecaster except strictly increasing one's own point total.
-In this final case, the only way for $i$ to increase their probability of being chosen as the best forecaster would be to increase the probability of scoring a point in $k^\prime$.
-The same logic as case 2 holds here that $i$ would then prefer to be truthful and maximize their expected score in $k^\prime$ to increase their probability of being selected as the best forecaster.
-\end{enumerate}
-
-Since any configuration of the $m-1$ events falls into one of these three cases, we have shown that any forecaster is weakly incentivized to report truthfully.
-To show that any forecaster is strongly incentivized to report truthfully, we simply show that $i$ believes cases 2 or 3 will happen with positive probability.
-Since $y_{j,k} = p_{j,k} \in (0,1) \forall j \forall k$, we know that every forecaster has some uncertainty on each event.
-As a result, we can conclude that $f_{j,k} > 0 \forall j \forall k$.
-We can think of all possible outcomes as the set of all possible binary strings of length $n$, and since $f_{j,k} > 0 \forall j \forall k$ there exists at least one sequence of outcomes strings picked from our set that constitutes cases 2 or 3.
-As a result, there is a positive probability that cases 2 or 3 occur, and thus forecasters are strongly incentivized to report truthfully.
-
-\subsection{Accuracy}
-
-% From Proposition 2 of \citet{witkowski2018incentive}, we have that $E_{x \sim \theta}(R_q(y, x)) = R_q(y, \theta) + \theta^2 - \theta$.
-Additionally, for a single event, a forecaster's accuracy $a_i$ is by definition just $R_q(y, \theta)$.
-So, $E_{x \sim \theta}(R_q(y, x)) = a_i + \theta^2 - \theta$.
-For a single event with probability $\theta$, forecaster $i$'s expected score is $\E_{x \sim \theta} f_i = E_{x \sim \theta}(R_q(y_i, x)) = a_i + \theta^2 - \theta$.
-
-% \subsection{Truthfulness for a single event}
-% (section 4.3, proposition 5).
-For forecaster $i$ to be selected, they either need to have $f_i = 1$, and then be chosen uniformly at random from all others who scored 1, or everyone must score 0 and they will be chosen uniformly at random.
-In the first case, the expected number of other forecasters who also score 1 is $\sum_{i' \neq i} \E_{x \sim \theta} f_{i'} = \sum_{i' \neq i} (a_{i'} + \theta^2 - \theta) = (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}$.
-Then, the probability that forecaster $i$ is chosen is
-% \[
-%   P(f_i = 1) \frac{1}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}} = \frac{a_i +\theta^2 - \theta}{1 + (n-1) (\theta^2 - \theta) \sum_{i' \neq i} a_{i'}}
-% \]
-% In the other case, the probability $i$ wins is just 
-% \[
-%   \frac{1}{n} \prod_{i} P(f_i = 0) = \frac{\prod_i (1 - a_i -\theta^2 + \theta)}{n}
-% \]
-
-% There's probably a better way to do this... Actually coming back to this I'm not even sure that the first step is allowed (using expected number of winners directly instead of summing over cases)
-
-% \subsection{Truthfulness for multiple events}
-\begin{theorem}
-  \label{shelf_bound}
-    $m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta}$
-\end{theorem}
-\emph{Proof:} This proof is a slight modification of the proof of Theorem 8 in \cite{witkowski2018incentive}.
-
-We first bound the difference in the expected number of wins of $i^*$ and $j$, for any $j \neq i^*$. 
-\begin{align*}
-  \E \left( \sum_{k=1}^m f_{i^*, k}\right) - \E \left( \sum_{k=1}^m f_{j, k}\right)
-  &= \left( \sum_{k=1}^m \E f_{i^*, k}\right) - \left( \sum_{k=1}^m \E f_{j, k}\right)\\
-  &= \sum_{k=1}^m \left(\E (f_{i^*, k}) - \E (f_{j, k})\right)\\
-  &= \sum_{k=1}^m \left((a_{i^*} + \theta_k^2 - \theta_k) - (a_j + \theta_k^2 - \theta_k)\right)\\
-  &= \sum_{k=1}^m \left(a_{i^*} - a_j\right)\\
-  &\geq \sum_{k=1}^m \epsilon\\
-  &=m \epsilon
-\end{align*}
-If $F_j \geq F_{i^*}$, then either $\E(F_{i^*}) - F_{i^*} \geq \frac{m \epsilon}{2}$ or $F_j - \E(F_j) \geq \frac{m \epsilon}{2}$.
-By Hoeffding's, we can upper bound the probability of each of these events by $2 e^{-\frac{2 (\frac{m \epsilon}{2})^2}{m}} = 2 e^{\frac{- m \epsilon^2}{2}}$.
-Using the union bound, the probability that either of those events occurs is twice this, or $4 e^{\frac{- m \epsilon^2}{2}}$.
-
-Using the union bound again over all $j \neq i$, we have 
-\begin{align*}
-  P(\shelf(y, x) = i) &= P(F_{i^*} > F_j \quad \forall j \neq i^*) \\
-                      &\geq 1 - \sum_{j\neq i^*} P(F_{i^*} \leq F_j) \\
-                      &= 1 - 4 (n-1) e^{\frac{- m \epsilon^2}{2}}
-\end{align*}
-
-Letting this quantity be $1 - \delta$ and solving for $m$, we see that this mechanism correctly chooses forecaster $i$ with probability $1 - \delta$ when $m$ is large enough to satisfy the inequality.
-Therefore
-\[ m_\delta(\shelf, n, \epsilon) \leq \frac{2}{\epsilon^2} \ln \frac{4(n-1)}{\delta} \]
-\hfill \QED
-
-Comparing this to the result of Theorem \ref{elf_bound}, we see that $\shelf$ is much more efficient than $\elf$.
-We can also directly apply the proof of Theorem \ref{shelf_bound} to $M_s$, since the mean and variance of $F_i$ is the same in both cases.
-Therefore, $m_\delta(\shelf, n, \epsilon) = m_\delta(M_s, n, \epsilon)$.
+Then, by Lemma 4 in [wagering mechanism paper], we have that forecaster $i$'s payout for an event will be 
+\[
+\frac{1}{n} + f(y_i, x) - \frac{1}{n-1} \sum_{j \neq i} f(y_j, x)
+\]
+where $f$ is a proper scoring rule whose values are contained in an interval of size $\frac{1}{n}$.
 
@@
 
-%\begin{thebibliography}{99}
-%\bibitem{elf} Witkowski, Freeman  \emph{Incentive-Compatible Forecasting Competitions} \url{https://las.inf.ethz.ch/files/witkowski-etal-aaai2018.pdf}.
-%
-%\bibitem{bnb} Raab, Steger  \emph{“Balls into Bins” — A Simple and Tight Analysis} \url{http://www.dblab.ntua.gr/~gtsat/collection/scheduling/Balls%20into%20Bins%20A%20Simple%20and%20Tight%20Anal.pdf}.
-%\end{thebibliography}
+\end{document}
 
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:
